\resheading{Experience}

\begin{description}
    \item 
        \ressubheading{\href{https://www.pixeesoft.ch}{Pixeesoft GmbH}}{Geneva, Switzerland}
            {Founder}{Aug 2018 -- Present}
            { \footnotesize
            \begin{itemize}
                \resitem[--]{Migrated a bare metal distributed system to Kubernetes on Google Cloud.}
                \resitem[--]{\textbf{Consulting: }}{Developed a step-by-step navigation for people with visual impairment.}
                \resitem[--]{\textbf{Consulting: }}{Developed a carsharing iOS application.}
                \resitem[--]{\textbf{Technologies: }}{Google Cloud, Kubernetes, Spring Boot, Kotlin, Python, Firebase, iOS, Swift}
            \end{itemize}
            }
            
    \item 
        \ressubheading{\href{https://www.myfuturity.com}{Futurity Lab AG}}{Geneva, Switzerland}
            {CTO}{Oct 2016 -- July 2018}
            { \footnotesize
            \begin{itemize}
                \resitem[--]{Oversaw hardware R\&D of state-of-the-art thermometer for fertility tracking.}
                \resitem[--]{Designed and developed a PoC for Bluetooth synchronization between an iOS device and the thermometer.}
                \resitem[--]{Designed and developed a PoC for a distributed system managing constant flow of data from end-user devices.}
                 \resitem[--]{\textbf{Technologies: }}{Google Cloud, Kubernetes, Spring Boot, Java, iOS, Swift, HIPAA Compliance}
            \end{itemize}
            }

    \item 
        \ressubheading{\href{https://www.msdit.cz}{Merck \& Co. Inc.}}{Prague, Czech Republic}
            {Associate Software Engineer in Machine Learning}{Oct 2015 -- Sep 2016}
            { \footnotesize
            \begin{itemize}
                \resitem[--]{Designed and developed a distributed system in the cloud gathering data from various sources (web, mobile, desktop).}
                \resitem[--]{Developed an iOS application for tracking domain specific KPIs.}
                \resitem[--]{Designed and developed an internal lunch recommendation engine for groups (internal hackathon).}
                \resitem[--]{\textbf{Technologies: }}{AWS, Spring Boot, Java, iOS, Swift, Python}
            \end{itemize}
            }

    \item 
        \ressubheading{\href{https://www.pyd.io}{Pydio (Abstrium S.รก.r.l)}}{Paris, France}
            {Mobile Applications Developer}{Jan 2015 -- Sep 2015}
            { \footnotesize
            \begin{itemize}
                \resitem[--]{Developed a networking layer SDK in pure Swift to communicate with the backend.}
                \resitem[--]{Developed a flexible table-to-grid UI framework for displaying files and folders. Released under Apache 2.0 license.}
                \resitem[--]{Developed a caching system with diff support for folder tree structure using Realm database.}
                \resitem[--]{\textbf{Technologies: }}{iOS, Swift, Realm}
            \end{itemize}
            }

    \item 
        \ressubheading{\href{https://www.casablanca.cz}{Casablanca INT s.r.o.}}{Prague, Czech Republic}
            {Mobile Applications Developer}{Jul 2011 -- Dec 2014}
            { \footnotesize
            \begin{itemize}
            	  \resitem[--]{Developed iOS and Android vehicle monitoring applications for Commander SYSTEMS.}
                \resitem[--]{Developed iOS application for VM administration in the first Czech public cloud offering BIG BLUE ONE.}
                \resitem[--]{Developed iOS applications for IPTV CCTV project pixee.tv.}
                \resitem[--]{\textbf{Technologies: }}{iOS, Objective-C, Swift, Android, Java}
            \end{itemize}
            }
\end{description}